---
title: "Final_Project_GroupC"
author: "Kramer, Rashid, and Stone"
date: "3/8/2021"
output:
  html_document:
    toc: true
    toc_depth: 4
    theme: cerulean
    highlight: textmate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Preamble: Loading packages and data

```{r, message=FALSE}
library(tidyverse)
library(ggplot2)
library(ISLR)
library(partykit)
library(caret)
library(rpart)
library(randomForest)
library(pROC)
```

### Import and Initial Data Prep
### Be sure to set working directory to source file location

```{r}

housing <- read.csv(file = "AmesHousing.csv", header = TRUE)

```


### 1. Exploratory Data Analysis

#### Identify general trends in sales prices across time, neighbourhood, and home characteristics

```{r}

#Code Here

```


### 2. Sales Price Prediction Model
> Tip: think about performance metrics other than MSE: MAE, relative error, etc.

#### A predictive model that uses housing sale prices 2006-2009.

```{r}

#Code Here

```

####Performance is evaluated against *appropriate validation methods*.

```{r}

#Code Here

```

#### Compare estimated prediction accuracy against actual performance of 2010 data.

```{r}

#Code Here

```


### 3. Home Features that are most Predictive of Sales Price.

```{r}

#Code Here

```

#### The Above Features Relation to Sales Price/

```{r}

#Code Here

```

### 4. Model's accracy across neighbourhoods (geographic variance)

```{r}

#Code Here

```

### 5. Renovation Value Calculator

```{r}

#Code Here

```










