---
title: "Final_Project_GroupC"
author: "Kramer, Rashid, and Stone"
date: "3/8/2021"
output:
  html_document:
    toc: true
    toc_depth: 4
    theme: cerulean
    highlight: textmate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Preamble: Loading packages and data

```{r, message=FALSE}
library(tidyverse)
library(ggplot2)
library(ISLR)
library(partykit)
library(caret)
library(rpart)
library(randomForest)
library(pROC)
```

### Import and Initial Data Prep
### Be sure to set working directory to source file location

```{r}
#bring in housing data
housing <- read.csv(file = "AmesHousing.csv", header = TRUE)

#check for NAs
sum(is.na(housing))

# Every record has an NA in some form. Will need to subset data. 
#Alley--possibly just switch NA for another value? They simply do not have an alley.
housing$Alley[is.na(housing$Alley)] = "DNE"
#Lot Front -- Change to 0? They simply do not have a front yard.
housing$Alley[is.na(housing$Alley)] = 0

#BSMT data--possibly just switch NA for another value? They simply do not have basements
#housing=na.omit(housing)

#replace NAs with zero



#verify NAs
sum(is.na(housing))

```


### 1. Exploratory Data Analysis (Anthony w/ assistance)

#### Identify general trends in sales prices across time, neighbourhood, and home characteristics

```{r}

#Code Here

```


### 2. Sales Price Prediction Model (Khadija w/ assistance)
> Tip: think about performance metrics other than MSE: MAE, relative error, etc.

#### A predictive model that uses housing sale prices 2006-2009. 

#####  Model 1 (Khadija)
```{r}

#Code Here

```

##### Model 2 (Khadija)
```{r}

#Code Here

```



##### Model 3 (Evan)
```{r}

#Code Here

```

##### Model 4 (Evan)
```{r}

#Code Here

```

##### Model 5 (Anthony)
```{r}

#Code Here

```

####Performance is evaluated against *appropriate validation methods*. (Evan)

```{r}

#Code Here

```

#### Compare estimated prediction accuracy against actual performance of 2010 data.(Evan)

```{r}

#Code Here

```


### 3. Home Features that are most Predictive of Sales Price.(Anthony)

```{r}

#Code Here

```

#### The Above Features Relation to Sales Price? (Anthony)

```{r}

#Code Here

```

### 4. Model's accracy across neighbourhoods (geographic variance) (Khadija)

```{r}

#Code Here

```

### 5. Renovation Value Calculator (Evan and Anthony)

```{r}

#Code Here

```










