---
title: "Final_Project_GroupC"
author: "Kramer, Rashid, and Stone"
date: "3/8/2021"
output:
  html_document:
    toc: true
    toc_depth: 4
    theme: cerulean
    highlight: textmate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Preamble: Loading packages and data

```{r, message=FALSE}
library(tidyverse)
library(ggplot2)
library(ggcorrplot)
library(ISLR)
library(partykit)
library(caret)
library(rpart)
library(randomForest)
library(pROC)
```

### Import and Initial Data Prep
### Be sure to set working directory to source file location

```{r}
#bring in housing data
housing <- read.csv(file = "AmesHousing.csv", header = TRUE)

#check for NAs
sum(is.na(housing))

 
# #BSMT Numeric--This may need to be addressed differently. You can have a basement without a bathroom, and zero values already exist.
# Bsmt.Full.Bath
# Bsmt.Half.Bath
#Garage.Yr.Blt data is a Year value may need to be adjusted.
#Mas.Vnr.Area

DNE.Cols = c(74,75,76,32,33,34,35,37,8,59,65,66,62,60)
zero.Cols = c(49,50,5,61,63,64,28)
zero.Cols.alt = c(36,38,39,40) #These are all from one record (1342). Maybe just omit the record?

for (i in DNE.Cols){
  housing[[i]][is.na(housing[[i]])] = "DNE"
}

for (i in zero.Cols){
  housing[[i]][is.na(housing[[i]])] = 0
}

for (i in zero.Cols.alt){
  housing[[i]][is.na(housing[[i]])] = 0
}

#verify NAs
sum(is.na(housing))

```


### 1. Exploratory Data Analysis (Anthony w/ assistance)

#### Identify general trends in sales prices across time, neighbourhood, and home characteristics

```{r}

col.vector = seq(2, 81, by=1) #We do not need the iOrder or PID value

for (i in col.vector){
  
  plots<-ggplot(data = housing,
              aes(x=SalePrice,y=housing[[i]]))+
  geom_line()+
  geom_point(x=which.max(housing[[i]]),
              y=max(housing[[i]]),aes(color="red"),
              show.legend = FALSE)+
  xlab("# Variables")+
  ylab("R-squared")+
  theme_bw()
  #print(plots)

}

numeric.cols <-housing[unlist(lapply(housing, is.numeric)) ] 
cor.housing.sales <- cor(numeric.cols[,-1:-2])
ggcorrplot(cor.housing.sales)

ta <- cor.housing.sales >= 0.8

if (cor.housing.sales >= 0.8){
  
}
```
Once the dataset has been scrubbed, initial exploratory data analysis is conducted. The first analysis is looking at all numeric vectors in the dataset and checking to see if there are any correlations between variables.
Correlations:
Total.Bsmt.SF   ~   X1st.Flr.SF     (0.80)
Gr.Liv.Area     ~   TotRms.AbvGrd   (0.81)
Garage.Cars     ~   Garage.Area     (0.89)

### 2. Sales Price Prediction Model (Khadija w/ assistance)
> Tip: think about performance metrics other than MSE: MAE, relative error, etc.

#### A predictive model that uses housing sale prices 2006-2009. 

#####  Model 1 (Khadija)
```{r}

#Code Here

```

##### Model 2 (Khadija)
```{r}

#Code Here

```



##### Model 3 (Evan)
```{r}

#Code Here

```

##### Model 4 (Evan)
```{r}

#Code Here

```

##### Model 5 (Anthony)
```{r}

#Code Here

```

####Performance is evaluated against *appropriate validation methods*. (Evan)

```{r}

#Code Here

```

#### Compare estimated prediction accuracy against actual performance of 2010 data.(Evan)

```{r}

#Code Here

```


### 3. Home Features that are most Predictive of Sales Price.(Anthony)

```{r}

#Code Here

```

#### The Above Features Relation to Sales Price? (Anthony)

```{r}

#Code Here

```

### 4. Model's accracy across neighbourhoods (geographic variance) (Khadija)

```{r}

#Code Here

```

### 5. Renovation Value Calculator (Evan and Anthony)

```{r}

#Code Here

```










